\bf Excuse me, do you have a moment to talk about version control?

### 2017-06-29 README.Rmd
Figure infrastructure: captions, references, etc.

@@

Many people who don't use Git unwittingly re-invent a poor man's version of it. Figure X depicts a hypothetical analysis of the iris data, captured in a single R source file. With informal version control, contributors create derivative copies of `iris.R`, decorating the file name with initials, dates, and other descriptors. Even when working alone, this leads to multiple versions of `iris.R` of indeterminate relatedness (Fig Xa). In collaborative settings based on email distribution, the original file swiftly becomes the root of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve (Fig Xb).

```{r echo = FALSE, out.width="100%"}
knitr::include_graphics("diy-vs-git-solo-vs-collab.png")
```

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message and a nickname. Figure Xc depicts this sort of linear *in situ* development. Figure Xd shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important 
versions get a human-readable tag, to signal a meaningful milestone. Yes, there 
is some pain in adopting the formalism of Git, but it is worth it.

```{r include = FALSE, echo = FALSE, out.width="100%"}
knitr::include_graphics("bartlett-copies-vs-commits.png")
```

@@

We've explored Git's powerful structure for file management, so where does GitHub fit in? [GitHub](https://github.com) complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. It is like DropBox or Google Drive, but more structured, powerful, and programmatic.

@@

```{r echo = FALSE, out.width="100%"}
knitr::include_graphics("your-repo-their-repo-central-remote-repo.png")
```

@@

Recall that a repository or repo is just a directory of files that Git manages holistically. A commit functions like a snapshot of all the files in the repo, at a specific moment. Under the hood, that is not exactly how Git implements things. Mental models don't have to be accurate in order to be useful, but in this case there's some value in aligning the two.

```{r echo = FALSE, out.width="100%"}
knitr::include_graphics("commit-diff-sha-tag.png")
```

Figure X is another look at our fictional analysis of the iris data, focusing on the evolution of its script `iris.R`. Consider version A of this file and a modified version, version B. Assume that version A was part of one Git commit and version B was part of the next commit. The set of differences between A and B is called a "diff" and Git users contemplate diffs a lot. Diff inspection is how you re-explain to yourself how version A differs from version B. Diff inspection is not limited to adjacent commits. You can inspect the diffs between any two commits.

@@

Every time you make a commit you must also write a short __commit message__. Ideally, this conveys the motivation for the change. Remember, the diff will show the content. When you revisit a project after a break or need to digest recent changes made by a colleague, looking at the __history__, by reading commit messages and skimming through diffs, is an extremely efficient way to get up to speed. Figure X shows the messages associated with the last three commits.

Every commit needs some sort of nickname, so you can identify it. Git does this automatically, assigning each commit what is called a SHA, a seemingly random string of 40 letters and numbers (it is not, in fact, random but is a SHA-1 checksum hash of the commit). Though you will be exposed to these, you don't have to handle them directly very often and, when you do, usually the first 7 characters suffice. The commit messages in Figure X are prefixed by such abbreviated SHAs. You can also designate certain snapshots as special with a __tag__, which is a name of your choosing. In a software project, it is typical to tag a release with its version, e.g., "v1.0.3". For a manuscript or analytical project, you might tag the version submitted to a journal or transmitted to external collaborators. Figure X shows a tag, "draft-01", associated with the last commit.

>>>>

```{r knitr_options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width = "100%")
```

@@

Many people who don't use Git unwittingly re-invent a poor man's version of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of the iris data, captured in a single R source file. With informal version control, contributors create derivative copies of `iris.R`, decorating the file name with initials, dates, and other descriptors. Even when working alone, this leads to multiple versions of `iris.R` of indeterminate relatedness (Figure \ref{fig:diy-vs-git}A). In collaborative settings based on email distribution, the original file swiftly becomes the root of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve Figure \ref{fig:diy-vs-git}B).

```{r diy-vs-git, fig.cap="\\label{fig:diy-vs-git}A: Solo work with DIY version control via filename. B: Collaborative work with DIY version control. C: Solo work with Git. D: Collaborative work with Git."}
knitr::include_graphics("diy-vs-git-solo-vs-collab.png")
```

The Git way is to track the evolution of `iris.R`, through a series of commits,
each equipped with an explanatory message. Figure \ref{fig:diy-vs-git}C depicts this linear, *in situ* development process. Figure \ref{fig:diy-vs-git}D shows the same history for a common collaborative Git workflow, where contributors work independently but sync regularly to a common version. Especially important 
versions get a human-readable tag, to signal a meaningful milestone. Yes, there 
is some pain in adopting the formalism of Git, but it is worth it.

@@

We've explored Git's powerful structure for file management, so where does GitHub fit in? [GitHub](https://github.com) complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.

@@

```{r yours-theirs-github, fig.cap = "\\label{fig:yours-theirs-github}With Git, all contributors have a copy of the repo, with all files and the full history. It is typical to stay in sync through the use of a central remote repo, such as GitHub. Hosted remotes like GitHub also provide access to the repo through a web browser."}
knitr::include_graphics("your-repo-their-repo-central-remote-repo.png")
```

@@

Recall that a repository or repo is just a directory of files that Git manages holistically. A commit functions like a snapshot of all the files in the repo, at a specific moment. Under the hood, that is not exactly how Git implements things. Although mental models don't have to be accurate in order to be useful, in this case it helps to align the two.

```{r commit-diff-sha-tag, fig.cap="\\label{fig:commit-diff-sha-tag}Partial commit history for our iris example."}
knitr::include_graphics("commit-diff-sha-tag.png")
```

Figure \ref{fig:commit-diff-sha-tag} is another look at our fictional analysis of the iris data, focusing on the evolution of its script, `iris.R`. Consider version A of this file and a modified version, version B. Assume that version A was part of one Git commit and version B was part of the next commit. The set of differences between A and B is called a "diff" and Git users contemplate diffs a lot. Diff inspection is how you re-explain to yourself how version A differs from version B. Diff inspection is not limited to adjacent commits. You can inspect the diffs between any two commits.

@@

Every time you make a commit you must also write a short __commit message__. Ideally, this conveys the motivation for the change. Remember, the diff will show the content. When you revisit a project after a break or need to digest recent changes made by a colleague, looking at the __history__, by reading commit messages and skimming through diffs, is an extremely efficient way to get up to speed. Figure \ref{fig:commit-diff-sha-tag} shows the messages associated with the last three commits.

Every commit needs some sort of nickname, so you can identify it. Git does this automatically, assigning each commit what is called a SHA, a seemingly random string of 40 letters and numbers (it is not, in fact, random but is a SHA-1 checksum hash of the commit). Though you will be exposed to these, you don't have to handle them directly very often and, when you do, usually the first 7 characters suffice. The commit messages in Figure \ref{fig:commit-diff-sha-tag}  are prefixed by such truncated SHAs. You can also designate certain snapshots as special with a __tag__, which is a name of your choosing. In a software project, it is typical to tag a release with its version, e.g., "v1.0.3". For a manuscript or analytical project, you might tag the version submitted to a journal or transmitted to external collaborators. Figure \ref{fig:commit-diff-sha-tag} shows a tag, "draft-01", associated with the last commit.

### 2017-06-29 README.tex
Figure infrastructure: captions, references, etc.

Many people who don't use Git unwittingly re-invent a poor man's version
of it. Figure X depicts a hypothetical analysis of the iris data,
captured in a single R source file. With informal version control,
contributors create derivative copies of \texttt{iris.R}, decorating the
file name with initials, dates, and other descriptors. Even when working
alone, this leads to multiple versions of \texttt{iris.R} of
indeterminate relatedness (Fig Xa). In collaborative settings based on
email distribution, the original file swiftly becomes the root of a
complicated phylogeny that no amount of ``Track changes'' and good
intentions can resolve (Fig Xb).

\includegraphics[width=1\linewidth]{diy-vs-git-solo-vs-collab}

The Git way is to track the evolution of \texttt{iris.R}, through a
series of commits, each equipped with an explanatory message and a
nickname. Figure Xc depicts this sort of linear \emph{in situ}
development. Figure Xd shows the same history for a common collaborative
Git workflow, where contributors work independently but sync regularly
to a common version. Especially important versions get a human-readable
tag, to signal a meaningful milestone. Yes, there is some pain in
adopting the formalism of Git, but it is worth it.

@@

We've explored Git's powerful structure for file management, so where
does GitHub fit in? \href{https://github.com}{GitHub} complements Git by
providing a slick user interface and distribution mechanism for Git
repositories. Git is the software you will use locally to record changes
to a set of files. GitHub is a hosting service that provides a Git-aware
home for such projects on the internet. It is like DropBox or Google
Drive, but more structured, powerful, and programmatic.

@@

\includegraphics[width=1\linewidth]{your-repo-their-repo-central-remote-repo}

@@

Recall that a repository or repo is just a directory of files that Git
manages holistically. A commit functions like a snapshot of all the
files in the repo, at a specific moment. Under the hood, that is not
exactly how Git implements things. Mental models don't have to be
accurate in order to be useful, but in this case there's some value in
aligning the two.

\includegraphics[width=1\linewidth]{commit-diff-sha-tag}

Figure X is another look at our fictional analysis of the iris data,
focusing on the evolution of its script \texttt{iris.R}. Consider
version A of this file and a modified version, version B. Assume that
version A was part of one Git commit and version B was part of the next
commit. The set of differences between A and B is called a ``diff'' and
Git users contemplate diffs a lot. Diff inspection is how you re-explain
to yourself how version A differs from version B. Diff inspection is not
limited to adjacent commits. You can inspect the diffs between any two
commits.

@@

Every time you make a commit you must also write a short \textbf{commit
message}. Ideally, this conveys the motivation for the change. Remember,
the diff will show the content. When you revisit a project after a break
or need to digest recent changes made by a colleague, looking at the
\textbf{history}, by reading commit messages and skimming through diffs,
is an extremely efficient way to get up to speed. Figure X shows the
messages associated with the last three commits.

Every commit needs some sort of nickname, so you can identify it. Git
does this automatically, assigning each commit what is called a SHA, a
seemingly random string of 40 letters and numbers (it is not, in fact,
random but is a SHA-1 checksum hash of the commit). Though you will be
exposed to these, you don't have to handle them directly very often and,
when you do, usually the first 7 characters suffice. The commit messages
in Figure X are prefixed by such abbreviated SHAs. You can also
designate certain snapshots as special with a \textbf{tag}, which is a
name of your choosing. In a software project, it is typical to tag a
release with its version, e.g., ``v1.0.3''. For a manuscript or
analytical project, you might tag the version submitted to a journal or
transmitted to external collaborators. Figure X shows a tag,
``draft-01'', associated with the last commit.

>>>>

Many people who don't use Git unwittingly re-invent a poor man's version
of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of
the iris data, captured in a single R source file. With informal version
control, contributors create derivative copies of \texttt{iris.R},
decorating the file name with initials, dates, and other descriptors.
Even when working alone, this leads to multiple versions of
\texttt{iris.R} of indeterminate relatedness (Figure
\ref{fig:diy-vs-git}A). In collaborative settings based on email
distribution, the original file swiftly becomes the root of a
complicated phylogeny that no amount of ``Track changes'' and good
intentions can resolve Figure \ref{fig:diy-vs-git}B).

\begin{figure}
\includegraphics[width=1\linewidth]{diy-vs-git-solo-vs-collab} \caption{\label{fig:diy-vs-git}A: Solo work with DIY version control via filename. B: Collaborative work with DIY version control. C: Solo work with Git. D: Collaborative work with Git.}\label{fig:diy-vs-git}
\end{figure}

The Git way is to track the evolution of \texttt{iris.R}, through a
series of commits, each equipped with an explanatory message. Figure
\ref{fig:diy-vs-git}C depicts this linear, \emph{in situ} development
process. Figure \ref{fig:diy-vs-git}D shows the same history for a
common collaborative Git workflow, where contributors work independently
but sync regularly to a common version. Especially important versions
get a human-readable tag, to signal a meaningful milestone. Yes, there
is some pain in adopting the formalism of Git, but it is worth it.

@@

We've explored Git's powerful structure for file management, so where
does GitHub fit in? \href{https://github.com}{GitHub} complements Git by
providing a slick user interface and distribution mechanism for Git
repositories. Git is the software you will use locally to record changes
to a set of files. GitHub is a hosting service that provides a Git-aware
home for such projects on the internet. These relationships are shown in
Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google
Drive, but more structured, powerful, and programmatic.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{your-repo-their-repo-central-remote-repo} \caption{\label{fig:yours-theirs-github}With Git, all contributors have a copy of the repo, with all files and the full history. It is typical to stay in sync through the use of a central remote repo, such as GitHub. Hosted remotes like GitHub also provide access to the repo through a web browser.}\label{fig:yours-theirs-github}
\end{figure}

@@

Recall that a repository or repo is just a directory of files that Git
manages holistically. A commit functions like a snapshot of all the
files in the repo, at a specific moment. Under the hood, that is not
exactly how Git implements things. Although mental models don't have to
be accurate in order to be useful, in this case it helps to align the
two.

\begin{figure}
\includegraphics[width=1\linewidth]{commit-diff-sha-tag} \caption{\label{fig:commit-diff-sha-tag}Partial commit history for our iris example.}\label{fig:commit-diff-sha-tag}
\end{figure}

Figure \ref{fig:commit-diff-sha-tag} is another look at our fictional
analysis of the iris data, focusing on the evolution of its script,
\texttt{iris.R}. Consider version A of this file and a modified version,
version B. Assume that version A was part of one Git commit and version
B was part of the next commit. The set of differences between A and B is
called a ``diff'' and Git users contemplate diffs a lot. Diff inspection
is how you re-explain to yourself how version A differs from version B.
Diff inspection is not limited to adjacent commits. You can inspect the
diffs between any two commits.

@@

Every time you make a commit you must also write a short \textbf{commit
message}. Ideally, this conveys the motivation for the change. Remember,
the diff will show the content. When you revisit a project after a break
or need to digest recent changes made by a colleague, looking at the
\textbf{history}, by reading commit messages and skimming through diffs,
is an extremely efficient way to get up to speed. Figure
\ref{fig:commit-diff-sha-tag} shows the messages associated with the
last three commits.

Every commit needs some sort of nickname, so you can identify it. Git
does this automatically, assigning each commit what is called a SHA, a
seemingly random string of 40 letters and numbers (it is not, in fact,
random but is a SHA-1 checksum hash of the commit). Though you will be
exposed to these, you don't have to handle them directly very often and,
when you do, usually the first 7 characters suffice. The commit messages
in Figure \ref{fig:commit-diff-sha-tag} are prefixed by such truncated
SHAs. You can also designate certain snapshots as special with a
\textbf{tag}, which is a name of your choosing. In a software project,
it is typical to tag a release with its version, e.g., ``v1.0.3''. For a
manuscript or analytical project, you might tag the version submitted to
a journal or transmitted to external collaborators. Figure
\ref{fig:commit-diff-sha-tag} shows a tag, ``draft-01'', associated with
the last commit.
